Report - Latest Rodent Data

### 2017-11-15 report.Rmd
missed case of changing period_code to most_recent_period

joined_data = left_join(sp_predictions, observed, by = "species")
joined_data[is.na(joined_data)] = 0
joined_data[joined_data$species=='total','abundance'] = sum(joined_data$abundance,na.rm=T)
joined_data[joined_data$species=='total','period'] = period_code

>>>>

joined_data = left_join(sp_predictions, observed, by = "species")
joined_data[is.na(joined_data)] = 0
joined_data[joined_data$species=='total','abundance'] = sum(joined_data$abundance,na.rm=T)
joined_data[joined_data$species=='total','period'] = most_recent_period
